### 2021-01-03 treatise-pdflatex/4_simulation.tex
Conversion: compile chap 3

In this chapter we shall compare \Rf {d:2:OL:H3} with numerical experiments.
For the convex optimization, we choose the Python library CVXPY \cite {DiB16}.
While a direct implementation of Algorithm [7] leads to extraordinarily large complexity, Candès and Romberg \cite {CaR05} showed that DS can be cast as a linear program, which we elaborate below.

@@

Let us represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathcal {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\mathcal {R} \SB {\V {x}}
\in \mathbb {R} ^{2M} \\
\mathcal {R} \SB {\V {x}} _{\SB {m}}
= \startcases
\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \\
\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \\
\stopcases \\
m' 
=  0, 1, 2, \ldots, M-1 \\
}
%
The injection is obvious, and we may define \m {\mathcal {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\mathcal {R} ^{-1} \SB {\mathcal {R} \SB {\V {x}}}
=\V {x} \\
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \mathbb {C} ^{M_1 \D M_2}}, define real representation \m {\mathcal {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\mathcal {R} \SB {\M {A}}
\in \mathbb {R} ^{2M_1 \D 2M_2} \\
\mathcal {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\startcases
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \\
-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \\
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
\stopcases \\
m_1 
= 0, 1, 2, \ldots, M_1 -1 \\
m_2 
= 0, 1, 2, \ldots, M_2 -1 \\
}

@@

\DispNum {y:y:Ry:Ny} {
\tilde {\V {y}}
= \mathcal {R} \SB {\V {y}}
\in \mathbb {R} ^{2 N_B^2} \\
%
\tilde {\V {g}}
= \mathcal {R} \SB {\V {g}}
\in \mathbb {R} ^{2 N_H^2} \\
%
\tilde {\M {P}}
= \mathcal {R} \SB {\M {P}}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\M {P}} ^\Adj
= \mathcal {R} \SB {\M {P} ^\Adj}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\V {z}}
= \mathcal {R} \SB {\V {z}}
\in \mathbb {R} ^{2 N_B^2} \\
}
%
so, by construction,
%
\DispNum {y:y:Pg:gz} {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} \\
}
%
And denote \m {\V {1}} to be the all-\m{1} vector, and \m {\V {0}} the all-\m{0} vector, whose dimension will be inferred from context.

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \mathbb {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \mathbb {C} ^{ N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
%
\item Define \m {\tilde {\V {y}}, \tilde {\V {g}}, \tilde {\M {P}}, \tilde {\M {P}} ^\Adj, \tilde {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
%
\item Compute the convex program
\DispNum {g:f:gf:S1} {
\hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
\leftarrow \startcases
   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  \MC \IP {\V {1}, \tilde {\V {f}}'} \\
   \mathrm {subject} \; \mathrm {to} \MC \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   \MC - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   \MC \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
   \MC - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
\stopcases \\
}
\item Convert
%
\DispNum {g:::R1:1g} {
\Hat{\V {g}}
\leftarrow \mathcal {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \\
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\hat {G}
\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} \\
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\hat {\M {H}}
\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger \\
}
\item Output \m {\hat {\M {H}}}.
\stopitemize
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Let \m {\g_{\mathrm {DS}} \geq 0} be given, and \m {\M {P}}

\item Set
\Disp {
N_0
=2 N_H^2, \\
N_2
=\lfloor 4 \log N_H \rfloor, \\
N_1
=\lfloor \R {N_0 N_2} \rfloor \\
}

@@

\item Apply Moore–Penrose inverse to \m {\V {y}, \M {P} _2} to get \m {\hat {\V {g}}_2}, which corresponds to \m {\hat {\V {g}}}.
\stopitemize
}

@@

To get some idea on the order of magnitude of noise-to-signal level, plug in some actual numbers.
Consider only path loss in the simplest form according to Friis Law.
Suppose the power of mobile phone antenna is \m {0.25} W,
the carrier frequency is \m {5} GHz,
the base station is \m {1.5} km away,
the noise is \m {–40} dB W.
If so, the noise-to-signal ratio is
\DispNum {1:8:02:24} {
10^{-4} \frac {1} {0.25} \R {\frac {5 \D 10^9 \D 4 \pi \D 1500} {3 \D 10^8}}
=0.224 \\
}

@@

We take \m {N_H} to be \m {12, 18, 24}, respectively.
For assorted plots, two series of plots are simulated.
The first series for \m {N_B = N_H}, giving \m {12, 18, 24}.
The second series for \m {N_B = \lfloor 5 N_H /6 \rfloor}, giving \m {10, 15, 20}.
The third series for \m {N_B = \lfloor 2 N_H /3 \rfloor}, giving \m {8, 12, 16}.
For plots of OMP only, we consider \m {N_B = \lfloor N_H \rfloor}.
For plots of DS only, we consider \m {N_B = \lfloor 5 N_H /6 \rfloor}.
On the other hand, \m {N_R} always set to be \m {\lfloor \RB {\log N_H}^2 \rfloor}.
Unfortunately, this is very far from achieving the ideal values \Rf {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.

@@

For performance metric, we follow Lee, Gil, and Lee \cite {LGL16},
\DispNum {h:h:lo:vg} {
\tilde {\chi}
=\RB {
   \frac {\log_2 {\VNm {\V {h} -\hat {\V {h}}} _2}}
   {\log_2 {\VNm {\V {h}}_2}}
} _{\mathsf {avg}}, \\
}
However, we note that when \m {\VNm {\V {h}}_2} is small, this can blow up.
We do not know either whether \m {\tilde {\chi}} is a good indicator of channel capacity; it seems to be, but actually we did not consider a definite a channel model in this treatise.

@@

\blank [big]
\externalfigure [assorted-square-small-error.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 12, N_H = 12}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-square-medium-error.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 18, N_H = 18}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-square-big-error.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 24, N_H = 24}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 10, N_H = 12}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 15, N_H = 18}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 20, N_H = 24}, error norm.}
%
\blank [big]
\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 8, N_H = 12}, error norm.}
%
\blank [big]
\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 12, N_H = 18}, error norm.}
%
\blank [big]
\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 16, N_H = 24}, error norm.}

As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
%
\blank [big]
\externalfigure [assorted-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
\caption {Assorted methods, \m {N_B = 15, N_H = 18}, time.}
\blank [big]

@@

Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
Here, \m {\tilde {\chi}} is shown too.
%
\blank [big]
\externalfigure [ddss-narrow-small-error.png] [wfactor=fit, hfactor=fit]
\caption {DS, \m {N_B = 10, N_H = 12}, error.}
\blank [big]
%
\blank [big]
\externalfigure [ddss-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
\caption {DS, \m {N_B = 15, N_H = 18}, error.}
\blank [big]
%
\blank [big]
\externalfigure [ddss-narrow-big-error.png] [wfactor=fit, hfactor=fit]
\caption {DS, \m {N_B = 20, N_H = 24}, error.}
\blank [big]
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
%
\blank [big]
\externalfigure [ddss-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
\caption {DS, \m {N_B = 15, N_H = 18}, time.}
\blank [big]

@@

%
\blank [big]
\externalfigure [oommpp-square-small-error.png] [wfactor=fit, hfactor=fit]
\caption {OMP, \m {N_H = 12, N_B = 12}, error.}
\blank [big]
%
\blank [big]
\externalfigure [oommpp-square-medium-error.png] [wfactor=fit, hfactor=fit]
\caption {OMP, \m {N_H = 18, N_B = 18}, error.}
\blank [big]
%
\blank [big]
\externalfigure [oommpp-square-big-error.png] [wfactor=fit, hfactor=fit]
\caption {OMP, \m {N_H = 24, N_B = 24}, error.}
\blank [big]
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
%
\blank [big]
\externalfigure [oommpp-square-medium-time.png] [wfactor=fit, hfactor=fit]
\caption {OMP, \m {N_H = 18, N_B = 18}, time.}
\blank [big]

@@

\blank [big]
\externalfigure [scatter-ddss-failure.png] [wfactor=300]
\caption {A scatter plot of position versus magnitude for a case in which DS failed.}
\blank [big]

\blank [big]
\externalfigure [scatter-ddss-success.png] [wfactor=300]
\caption {A scatter plot of position versus magnitude for a case in which DS succeeded.}
\blank [big]

@@

We attemp to give a heuristic argument regarding the complexity of Newton steps.
We say the function being minimized is \m {\VNm {\V {g}}_1}.
Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
Then Boyd and Vandenberghe \cite {BoV04} (p.505, Eqn.9.56) gave a bound of the number of steps.
If we just take that as the complexity bound for DS, it becomes
%
\DispNum {C:S:C0:1e'} {
C_{\mathrm {DS}}
= \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
+ \log_2 \log_2 \frac {1} {\e}} C_{\mathrm {step}} \\
}
%
Here \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error, and \m {C_{\mathrm {step}}} is the complexity of Newton step.
According to their analysis (Eqn.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
Also, \m {C_0} usually assumes the value of about several hundred.
There was an example they gave in which \m {C_0 =375}, where, with their notation,
\m {C_0 =(20 -8\a) / (\a \b \RB {1 -2\a}^2}), where \m {\a = 0.1, \b = 0.8, \e =0.01}, and \m {\a, \b} are parameters used in the Backtrack Line Tracing algorithm).

@@

We take some liberty to assume that, at the start the iteration, the Moore–Penrose inverse was taken to be the initial value of \m {\V {g}_0}, namely
%
\DispNum {g:0:gL:Py} {
\V {g}_0
=\V {g}_{\mathrm {LS}} \\
= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} \\
}
%
By above, we may write the complexity of DS to be
%
\DispNum {C:S:Og:g1} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \\
}
%
Also assume
%
\DispNum {g:g:g;:;g} {
\V {g} ^\star
\approx \V {g} \\
}
%
Indeed, this is the main thesis of our investigation.
And by restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so
%
\DispNum {P:P:IN:H2} {
\M {P} ^\dagger \M {P}
\approx I _{N_{H}^2} \\
}
%
Thus, by \Rf {g:0:gL:Py}, \Rf {C:S:Og:g1}, and \Rf {g:g:g;:;g},
%
\DispNum {C:S:Og:z1} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {
   \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
   -\V {g}} _1} N_H^4 \\
=\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \\
}

We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
= \s \mathcal {O} \RB {1} \\
}
Then we simply have
%
\DispNum {C:S:ON:H6} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {N_{H}^6} \\
}

On the other hand, Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}.
They gave
%
\DispNum {C:P:ON:NY} {
C_{\mathrm {OMP}}
=\mathcal {O} \SB {N_H^2 \log N_B} \\
}
%
Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\mathcal {O} \SB {N_H^2}}.

@@

\DispNum {t:P:NH:83} {
\tilde {t}_{\mathrm {OMP}} \eqsim \mathcal {O} \SB {N_H^{3.6}} \\
\tilde {t}_{\mathrm {Lasso}} \eqsim \mathcal {O} \SB {N_H^{4.8}} \\
\tilde {t}_{\mathrm {DS}} \eqsim \mathcal {O} \SB {N_H^{8.3}} \\
}

>>>>

In this chapter we shall compare \eqref {d:2:OL:H3} with numerical experiments.
For the convex optimization, we choose the Python library CVXPY \cite {DiB16}.
While a direct implementation of Algorithm [7] leads to extraordinarily large complexity, Candès and Romberg \cite {CaR05} showed that DS can be cast as a linear program, which we elaborate below.

@@

Let us represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathcal {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\mathcal {R} \SB {\V {x}}
\in \mathbb {R} ^{2M} \\
\mathcal {R} \SB {\V {x}} _{\SB {m}}
= \begin {cases}
\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, & m =2m' \\
\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, & m =2m'+1 \\
\end {cases} \\
m' 
=  0, 1, 2, \ldots, M-1 
}
%
The injection is obvious, and we may define \m {\mathcal {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\mathcal {R} ^{-1} \SB {\mathcal {R} \SB {\V {x}}}
=\V {x} 
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \mathbb {C} ^{M_1 \D M_2}}, define real representation \m {\mathcal {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\mathcal {R} \SB {\M {A}}
\in \mathbb {R} ^{2M_1 \D 2M_2} \\
\mathcal {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\begin {cases}
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \\
-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \\
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
\end {cases} \\
m_1 
= 0, 1, 2, \ldots, M_1 -1 \\
m_2 
= 0, 1, 2, \ldots, M_2 -1 
}

@@

\DispNum {y:y:Ry:Ny} {
\tilde {\V {y}}
= \mathcal {R} \SB {\V {y}}
\in \mathbb {R} ^{2 N_B^2} \\
%
\tilde {\V {g}}
= \mathcal {R} \SB {\V {g}}
\in \mathbb {R} ^{2 N_H^2} \\
%
\tilde {\M {P}}
= \mathcal {R} \SB {\M {P}}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\M {P}} ^\Adj
= \mathcal {R} \SB {\M {P} ^\Adj}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\V {z}}
= \mathcal {R} \SB {\V {z}}
\in \mathbb {R} ^{2 N_B^2} 
}
%
so, by construction,
%
\Disp {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} 
}
%
And denote \m {\V {1}} to be the all-\m{1} vector, and \m {\V {0}} the all-\m{0} vector, whose dimension will be inferred from context.

@@

\Result
{Algorithm}
{
\begin {itemize}
\item Input \m{\M {P} \in \mathbb {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \mathbb {C} ^{ N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
%
\item Define \m {\tilde {\V {y}}, \tilde {\V {g}}, \tilde {\M {P}}, \tilde {\M {P}} ^\Adj, \tilde {\V {z}}}, according to \eqref {y:y:Ry:Ny}.
%
\item Compute the convex program
\DispNum {g:f:gf:S1} {
\hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
\leftarrow \begin {cases}
   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  & \IP {\V {1}, \tilde {\V {f}}'} \\
   \mathrm {subject} \; \mathrm {to} & \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   & - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   & \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
   & - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
\end {cases} 
}
\item Convert
%
\DispNum {g:::R1:1g} {
\Hat{\V {g}}
\leftarrow \mathcal {R} ^{-1} \SB {\Hat{\T{\V {g}}}} 
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\hat {G}
\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} 
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\hat {\M {H}}
\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger 
}
\item Output \m {\hat {\M {H}}}.
\end {itemize}
}

@@

\Result
{Algorithm}
{
\begin {itemize}
\item Let \m {\g_{\mathrm {DS}} \geq 0} be given, and \m {\M {P}}

\item Set
\Disp {
N_0
=2 N_H^2, \\
N_2
=\lfloor 4 \log N_H \rfloor, \\
N_1
=\lfloor \R {N_0 N_2} \rfloor 
}

@@

\item Apply Moore–Penrose inverse to \m {\V {y}, \M {P} _2} to get \m {\hat {\V {g}}_2}, which corresponds to \m {\hat {\V {g}}}.
\end {itemize}
}

@@

To get some idea on the order of magnitude of noise-to-signal level, plug in some actual numbers.
Consider only path loss in the simplest form according to Friis Law.
Suppose the power of mobile phone antenna is \m {0.25} W,
the carrier frequency is \m {5} GHz,
the base station is \m {1.5} km away,
the noise is \m {–40} dB W.
If so, the noise-to-signal ratio is
\DispNum {1:8:02:24} {
10^{-4} \frac {1} {0.25} \R {\frac {5 \D 10^9 \D 4 \pi \D 1500} {3 \D 10^8}}
=0.224 
}

@@

We take \m {N_H} to be \m {12, 18, 24}, respectively.
For assorted plots, two series of plots are simulated.
The first series for \m {N_B = N_H}, giving \m {12, 18, 24}.
The second series for \m {N_B = \lfloor 5 N_H /6 \rfloor}, giving \m {10, 15, 20}.
The third series for \m {N_B = \lfloor 2 N_H /3 \rfloor}, giving \m {8, 12, 16}.
For plots of OMP only, we consider \m {N_B = \lfloor N_H \rfloor}.
For plots of DS only, we consider \m {N_B = \lfloor 5 N_H /6 \rfloor}.
On the other hand, \m {N_R} always set to be \m {\lfloor \RB {\log N_H}^2 \rfloor}.
Unfortunately, this is very far from achieving the ideal values \eqref {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.

@@

For performance metric, we follow Lee, Gil, and Lee \cite {LGL16},
\DispNum {h:h:lo:vg} {
\tilde {\chi}
=\RB {
   \frac {\log_2 {\VNm {\V {h} -\hat {\V {h}}} _2}}
   {\log_2 {\VNm {\V {h}}_2}}
} _{\mathsf {avg}}, 
}
However, we note that when \m {\VNm {\V {h}}_2} is small, this can blow up.
We do not know either whether \m {\tilde {\chi}} is a good indicator of channel capacity; it seems to be, but actually we did not consider a definite a channel model in this treatise.

@@

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-square-small-error.png}
\caption {Assorted methods, \m {N_B = 12, N_H = 12}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-square-medium-error.png}
\caption {Assorted methods, \m {N_B = 18, N_H = 18}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-square-big-error.png}
\caption {Assorted methods, \m {N_B = 24, N_H = 24}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-narrow-small-error.png}
\caption {Assorted methods, \m {N_B = 10, N_H = 12}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-narrow-medium-error.png}
\caption {Assorted methods, \m {N_B = 15, N_H = 18}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-narrow-big-error.png}
\caption {Assorted methods, \m {N_B = 20, N_H = 24}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-wide-small-error.png}
\caption {Assorted methods, \m {N_B = 8, N_H = 12}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-wide-medium-error.png}
\caption {Assorted methods, \m {N_B = 12, N_H = 18}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-wide-big-error.png}
\caption {Assorted methods, \m {N_B = 16, N_H = 24}, error norm.}
\end {figure}

As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-narrow-medium-time.png}
\caption {Assorted methods, \m {N_B = 15, N_H = 18}, time.}
\end {figure}

@@

Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
Here, \m {\tilde {\chi}} is shown too.
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {ddss-narrow-small-error.png}
\caption {DS, \m {N_B = 10, N_H = 12}, error.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {ddss-narrow-medium-error.png}
\caption {DS, \m {N_B = 15, N_H = 18}, error.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {ddss-narrow-big-error.png}
\caption {DS, \m {N_B = 20, N_H = 24}, error.}
\end {figure}
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {ddss-narrow-medium-time.png}
\caption {DS, \m {N_B = 15, N_H = 18}, time.}
\end {figure}

@@

%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {oommpp-square-small-error.png}
\caption {OMP, \m {N_H = 12, N_B = 12}, error.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {oommpp-square-medium-error.png}
\caption {OMP, \m {N_H = 18, N_B = 18}, error.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {oommpp-square-big-error.png}
\caption {OMP, \m {N_H = 24, N_B = 24}, error.}
\end {figure}
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {oommpp-square-medium-time.png}
\caption {OMP, \m {N_H = 18, N_B = 18}, time.}
\end {figure}

@@

\bigskip
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {scatter-ddss-failure.png}
\caption {A scatter plot of position versus magnitude for a case in which DS failed.}
\end {figure}
%
\begin {figure} [hbt]
\caption {A scatter plot of position versus magnitude for a case in which DS succeeded.}
\includegraphics [width = \textwidth] {scatter-ddss-success.png}
\end {figure}
\bigskip

@@

We attemp to give a heuristic argument regarding the complexity of Newton steps.
We say the function being minimized is \m {\VNm {\V {g}}_1}.
Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
Then Boyd and Vandenberghe \cite {BoV04} (p.505, Eqn.9.56) gave a bound of the number of steps.
If we just take that as the complexity bound for DS, it becomes
%
\DispNum {C:S:C0:1e'} {
C_{\mathrm {DS}}
= \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
+ \log_2 \log_2 \frac {1} {\e}} C_{\mathrm {step}} 
}
%
Here \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error, and \m {C_{\mathrm {step}}} is the complexity of Newton step.
According to their analysis (Eqn.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
Also, \m {C_0} usually assumes the value of about several hundred.
There was an example they gave in which \m {C_0 =375}, where, with their notation,
\m {C_0 =(20 -8\a) / (\a \b \RB {1 -2\a}^2}), where \m {\a = 0.1, \b = 0.8, \e =0.01}, and \m {\a, \b} are parameters used in the Backtrack Line Tracing algorithm).

@@

We take some liberty to assume that, at the start the iteration, the Moore–Penrose inverse was taken to be the initial value of \m {\V {g}_0}, namely
%
\DispNum {g:0:gL:Py} {
\V {g}_0
=\V {g}_{\mathrm {LS}} \\
= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} 
}
%
By above, we may write the complexity of DS to be
%
\DispNum {C:S:Og:g1} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 
}
%
Also assume
%
\DispNum {g:g:g;:;g} {
\V {g} ^\star
\approx \V {g} 
}
%
Indeed, this is the main thesis of our investigation.
And by restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so
%
\DispNum {P:P:IN:H2} {
\M {P} ^\dagger \M {P}
\approx I _{N_{H}^2} 
}
%
Thus, by \eqref {g:0:gL:Py}, \eqref {C:S:Og:g1}, and \eqref {g:g:g;:;g},
%
\DispNum {C:S:Og:z1} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {
   \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
   -\V {g}} _1} N_H^4 \\
=\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 
}

We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
= \s \mathcal {O} \RB {1} 
}
Then we simply have
%
\DispNum {C:S:ON:H6} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {N_{H}^6} 
}

On the other hand, Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}.
They gave
%
\DispNum {C:P:ON:NY} {
C_{\mathrm {OMP}}
=\mathcal {O} \SB {N_H^2 \log N_B} 
}
%
Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\mathcal {O} \SB {N_H^2}}.

@@

\DispNum {t:P:NH:83} {
\tilde {t}_{\mathrm {OMP}} \eqsim \mathcal {O} \SB {N_H^{3.6}} \\
\tilde {t}_{\mathrm {Lasso}} \eqsim \mathcal {O} \SB {N_H^{4.8}} \\
\tilde {t}_{\mathrm {DS}} \eqsim \mathcal {O} \SB {N_H^{8.3}} 
}
